\Large Analyzing the Supreme Court Citation Network

### 2017-12-30 Tex/paper.tex
revising literature setup

>>>>

Theorizing that legal citations arise through network interdependence processes  represents a potential contribution to the literature. To demonstrate the value of our contribution we must also incorporate established non-network processes that have been found to affect legal citations. We incorporate these processes through the specification of $h_{covariate}$ to be included in the c-TERGM.
